---
title: "Reproducible Pitch Presentation"
author: "Rasul Balayev"
date: "2/1/2021"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

##  Reproducible Pitch Presentation Project
This presentation is a part of Developing Data Products course's Final Assignment. For this project shinny app Diamond created. This app predicts the price of diamond based on inputs given by user.

## How to use app
By using diamond library, system fits a linear model to predict the price of diamond based on the carat

Application link: https://lavecchiasignora.shinyapps.io/Diamond/

Github repository for codes : https://github.com/LaVecchiaSignora/ShinyApp


## Dataset
Diamond dataset in UsingR is used

```{r, include=FALSE}
library(UsingR)
data(diamond)
```

```{r summary}
str(diamond)
```

## Slide with Plot

```{r, include=FALSE}
library(plotly)
```

```{r, echo=FALSE}
plot_ly(diamond, x = ~carat, y = ~price, type = "scatter", mode="markers")
```
